### 2016-04-04 docs/ms_communitySynchrony_PREPRINT.tex
adds preprint version of ms

\usepackage{lineno}
\linenumbers
\usepackage{setspace}
\usepackage{todonotes}
\doublespacing
\usepackage{color}
\usepackage{rotating}

@@

\normalsize{Andrew T. Tredennick\textsuperscript{1}, Claire de Mazancourt\textsuperscript{2}, Michel Loreau\textsuperscript{2}, and Peter B. Adler\textsuperscript{1}}

@@

\textbf{Keywords}: synchrony, compensatory dynamics, environmental stochasticity, demographic stochasticity, interspecific competition, stability

\textbf{Authorship}: ATT, CdM, and PBA designed the research. CdM and ML designed and analyzed the theoretical model. ATT and PBA performed the empirical analysis. All authors contributed to the interpretation and presentation of results. ATT wrote the first draft of the manuscript, and all authors contributed to manuscript revisions.

\textbf{Running Title}: Drivers of species synchrony in natural plant communities

\textbf{Article Type}: Letter

\textbf{Number of Words}: Abstract = 138; Main Text = 4965 (including section titles and in-line citations)

\textbf{Number of References}: 46

\textbf{Number of Tables and Figures}:  2 Tables;  3 Figures

\textbf{Corresponding Author}: \\
\hspace{2em}Andrew Tredennick \\  
\hspace{2em}Department of Wildland Resources and the Ecology Center\\
\hspace{2em}Utah State University \\
\hspace{2em}5230 Old Main Hill \\
\hspace{2em}Logan, Utah 84322 USA \\
\hspace{2em}Phone: +1-970-443-1599 \\
\hspace{2em}Fax: +1-435-797-3796 \\
\hspace{2em}Email: atredenn@gmail.com

@@

\begin{abstract}
Temporal asynchrony among species is an important mechanism through which diversity can stabilize ecosystem functioning, but identifying the mechanisms that determine synchrony remains a challenge.
Here, we refine and test theory showing that synchrony depends on three factors: species responses to environmental variation, interspecific competition, and demographic stochasticity. We then conduct simulation experiments with empirical population models to quantify the relative importance of these factors in five plant communities.
Simulation experiments showed that the average synchrony of per capita growth rates, which can range from 0 (perfect asynchrony) to 1 (perfect synchrony), was higher when environmental variation was present (0.62) rather than absent (0.43).
Removing interspecific competition and demographic stochasticity had small effects on synchrony. In these plant communities, where species interactions and demographic stochasticity have little influence, synchrony reflects the covariance in species responses to the environment.
\end{abstract}

\newpage{} \setlength{\parindent}{5ex}

@@

>>>>

\usepackage{setspace}
\usepackage{todonotes}
\usepackage{color}
\usepackage{rotating}

@@

\normalsize{Andrew T. Tredennick\textsuperscript{1}\footnote{Correspondence: Email: atredenn@gmail.com}, Claire de Mazancourt\textsuperscript{2}, Michel Loreau\textsuperscript{2}, and Peter B. Adler\textsuperscript{1}}

@@

@@

\begin{abstract}
Temporal asynchrony among species is an important mechanism through which diversity can stabilize ecosystem functioning, but identifying the mechanisms that determine synchrony remains a challenge.
Here, we refine and test theory showing that synchrony depends on three factors: species responses to environmental variation, interspecific competition, and demographic stochasticity. We then conduct simulation experiments with empirical population models to quantify the relative importance of these factors in five plant communities.
Simulation experiments showed that the average synchrony of per capita growth rates, which can range from 0 (perfect asynchrony) to 1 (perfect synchrony), was higher when environmental variation was present (0.62) rather than absent (0.43).
Removing interspecific competition and demographic stochasticity had small effects on synchrony. In these plant communities, where species interactions and demographic stochasticity have little influence, synchrony reflects the covariance in species responses to the environment.

\noindent{}\textbf{Keywords}\\
\noindent{}synchrony, compensatory dynamics, environmental stochasticity, demographic stochasticity, interspecific competition, stability
\end{abstract}

\setlength{\parindent}{5ex}

@@

\subsection{STATEMENT OF AUTHORSHIP}
ATT, CdM, and PBA designed the research. CdM and ML designed and analyzed the theoretical model. ATT and PBA performed the empirical analysis. All authors contributed to the interpretation and presentation of results. ATT wrote the first draft of the manuscript, and all authors contributed to manuscript revisions.
